Case-based Arabic Morphological Analysis

### 2010-12-16 tex/sarf.aclhlt.tex
acl hlt

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu

\documentclass[11pt,letterpaper]{article}
\usepackage{arabtex}
\usepackage{naaclhlt2010}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage{caption}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{color}
\usepackage{rotate}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{amsthm}
\usepackage{booktabs}

\usepackage{relsize}
\usepackage{fancyvrb}
%\usepackage{times}
\usepackage{latexsym}
\usepackage[colorlinks=false]{hyperref}

@@

\newcommand{\CharCodeIn}[1]{`\CodeIn{#1}'}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
\newcommand{\frl}[1]{\fbox{\RL{#1}}} 
\newcommand{\noArRL}[1]{\arabfalse\RL{#1}\arabtrue} 
\newcommand{\noTrRL}[1]{\transfalse\RL{#1}\transtrue}

\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

\author{ Jad Makhlouta \\
  \And
Hamza Harkous \\
  American University of Beirut \\
  {\tt \{jem04, hhh20, fz11\}@aub.edu.lb }
  \And 
  Fadi Zaraket 
}

@@

\begin{document}
\maketitle

\begin{abstract}
Natural language processing uses morphological 
analysis to abstract and annotate text.
Often times, and in particular in the context
of the Arabic language, annotations resulting from 
an ongoing branch of morphological analysis may not be
appropriate for the case study at hand. 
In this paper we present Sarf, a case based morphological 
analyzer for Arabic text. 
Sarf allows a case-based controller to control and refine
the state of the analysis on the fly. 
It uses compositional non-deterministic finite state machines 
to analyze a stream of text. 
Each alive machine corresponds to a valid analysis. 
Sarf uses concatenative analysis based on recursive affixes 
to better preserve part of speech information.
We automated the analysis of three books of Islamic
narrations (hadith) using Sarf where we
abstracted each book into a vector of complex structures.
Our results show high accuracy and efficiency.
%compared to
%state of the art analyzers. 
\end{abstract}

@@

\novocalize
The accuracy of the solutions suffer due to inherent difficulties
of morphological analysis of the Arabic language. 
For example, it is common practice to write Arabic text
without short vowels. 
This greatly increases the ambiguity of Arabic text. 
Another difficulty is that  Arabic letters can have up to 
four different forms
corresponding to their position in a word, i.e, beginning,
middle, end of word forms and separate forms. 
This allows the phrase \transfalse
\RL{il_A\nospace almdrsT} \transtrue
to be visually recognizable
as two separate words \RL{il_A} (to) and \RL{almdrsT} (the school) 
without the need of a delimiter such as a space in between. 
This happens because the first word \RL{almdrsT} ends with
\RL{T} a non-connecting letter. 
These words occur often in text and greatly increase the
difficulty of tokenization and are referred to as 
``run-on'' words~\cite{Buckwalter:04}.

@@

\transfalse
\begin{figure}[tb]
\center{
\resizebox{1.2\columnwidth}{!}
{ \input{psfigs/exhadith.pstex_t}}
\caption{Hadith abstraction example.}
\label{f:exhadith}
}
\end{figure}
% the FSMs for the three words
\transtrue

@@

\transfalse
\begin{figure*}[tb]
\center{
\resizebox{1.7\columnwidth}{!}
{ \input{psfigs/FSM.pstex_t}}
\caption{Example composition of the prefix, stem and suffix transducers.}
\label{f:example}
}
\end{figure*}
% the FSMs for the three words
\transtrue

@@

\begin{figure*}[tb]
\center{
\resizebox{1.8\columnwidth}{!}
{ \input{psfigs/abstract_machine.pstex_t}}
\caption{An abstraction of the non-deterministic composition of 
    the prefix, stem and suffix transducers.}
\label{f:composition}
}
\end{figure*}

@@

\begin{figure}[tb!]
\center{
\resizebox{.9\columnwidth}{!}
{ \input{psfigs/hadith.pstex_t}}
\caption{The controller of the hadith case study.}
\label{f:hadith}
}
\end{figure}

@@

\section{Acknoledgements}
\label{sec:acc}
We thank the Lebanese National Council for Scientific Research (LNCSR) for funding this research.

@@

\bibliographystyle{naaclhlt2010}
{\small \bibliography{fzAr}}

>>>>

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu
\documentclass[11pt]{article}
\usepackage{acl-hlt2011}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\usepackage{arabtex}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{color}
\usepackage{rotate}
\usepackage{rotating}
\usepackage{amsthm}
\usepackage{booktabs}

\usepackage{relsize}
\usepackage{fancyvrb}
\usepackage[colorlinks=false]{hyperref}

@@

%\newcommand{\CharCodeIn}[1]{`\CodeIn{#1}'}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
\newcommand{\frl}[1]{\fbox{\RL{#1}}} 
\newcommand{\noArRL}[1]{\arabfalse\RL{#1}\arabtrue} 
\newcommand{\noTrRL}[1]{\transfalse\RL{#1}\transtrue}

@@

%\author{ Jad Makhlouta \\\And
%Hamza Harkous \\
%  American University of Beirut \\
%  {\tt \{jem04, hhh20, fz11\}@aub.edu.lb } \\\And 
%  Fadi Zaraket 
%}

@@

\begin{document}
\maketitle
\begin{abstract}
Natural language processing uses morphological 
analysis to abstract and annotate text.
Often times, and in particular in the context
of the Arabic language, annotations resulting from 
an ongoing branch of morphological analysis may not be
appropriate for the case study at hand. 
In this paper we present Sarf, a case based morphological 
analyzer for Arabic text. 
Sarf allows a case-based controller to control and refine
the state of the analysis on the fly. 
It uses compositional non-deterministic finite state machines 
to analyze a stream of text. 
Each alive machine corresponds to a valid analysis. 
Sarf uses concatenative analysis based on recursive affixes 
to better preserve part of speech information.
We automated the analysis of three books of Islamic
narrations (hadith) using Sarf where we
abstracted each book into a vector of complex structures.
Our results show high accuracy and efficiency.
\end{quote}
\end{abstract}

@@

\novocalize
The accuracy of the solutions suffer due to inherent difficulties
of morphological analysis of the Arabic language. 
For example, it is common practice to write Arabic text
without short vowels. 
This greatly increases the ambiguity of Arabic text. 
Another difficulty is that  Arabic letters can have up to 
four different forms
corresponding to their position in a word, i.e, beginning,
middle, end of word forms and separate forms. 
This allows the phrase \transfalse
\RL{il_A\nospace almdrsT} \transtrue
to be visually recognizable
as two separate words \RL{il_A} (to) and \RL{almdrsT} (the school) 
without the need of a delimiter such as a space in between. 
This happens because the first word \RL{il_A} ends with
\RL{_A} a non-connecting letter. 
These words occur often in text and greatly increase the
difficulty of tokenization and are referred to as 
``run-on'' words~\cite{Buckwalter:04}.

@@

\transfalse
\begin{figure}[tb]
\center{
\resizebox{1.2\columnwidth}{!}
{ \input{figs/exhadith.pdftex_t}}
\caption{Hadith abstraction example.}
\label{f:exhadith}
}
\end{figure}
% the FSMs for the three words
\transtrue

@@

\transfalse
\begin{figure*}[tb]
\center{
\resizebox{1.7\columnwidth}{!}
{ \input{figs/FSM.pdftex_t}}
\caption{Example composition of the prefix, stem and suffix transducers.}
\label{f:example}
}
\end{figure*}
% the FSMs for the three words
\transtrue

@@

\begin{figure*}[tb]
\center{
\resizebox{1.8\columnwidth}{!}
{ \input{figs/abstract_machine.pdftex_t}}
\caption{An abstraction of the non-deterministic composition of 
    the prefix, stem and suffix transducers.}
\label{f:composition}
}
\end{figure*}

@@

\begin{figure}[tb!]
\center{
\resizebox{.9\columnwidth}{!}
{ \input{figs/hadith.pdftex_t}}
\caption{The controller of the hadith case study.}
\label{f:hadith}
}
\end{figure}

@@

%\section{Acknoledgements}
%\label{sec:acc}
%We thank the Lebanese National Council for Scientific Research (LNCSR) for funding this research.

@@

%\bibliographystyle{naaclhlt2010}
\bibliographystyle{acl}
{\small \bibliography{fzAr}}
